---
title: "Dictionary"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

### List of functions
General bits

1.	help(topic) – search r studio for tips on a function for topic by clicking “Help” on the bottom right panel and performing a search under “Topic”; similar to “?topic”.
2.	?topic - search r studio for tips on a function for topic by typing “?[insert topic name here]” in the Console; similar to “help(topic)”.
3.	ls() – shows a list of characters used by the user.
4.	dir() – shows a list of files; see list.files().
5.	list.files() – shows a list of files; dir().
Input and output
1.	save() – saves a data.
2.	load() – loads data that was previously saved using “save()”.
3.	data() – loads data.
4.	library() – downloads packages unto r studio.
5.	read.table() – turns data from a file into a table.
6.	read.csv() – turns data from a csv into a table.
7.	scan() – turns data from a file into a list.
8.	print() – returns argument.
9.	cat() – turns data into a string and concatenates them, before returning them to the argument.
10.	write.table() – turns data into a matrix before returning it to argument and turning it into a file.
Data Creation
1.	c() – concatenates variables into a vector.
2.	from:to (where from and to are replaced with numbers, e.g. 1:10) – to include numbers “from” to “to” (e.g. to include numbers 1 to 10).
3.	seq() – a sequence of number “from” one number “to” another.
4.	rep() – repeats a value.
5.	data.frame() – a matrix
6.	list() – holds list of variables.
7.	matrix() – a dataframe.
8.	factor() – categorizes a vector as a factor.
9.	rbind() – concatenates vectors into a row in a dataframe.
10.	cbind() – concatenates vectors into column in a dataframe.

```{r}

```
### Slicing and extracting data
Indexing vectors

1.	x[n] nth element
2.	x[-n] all but nth element
3.	x[1:n] first n elements
4.	x[-(1:n)] elements from n+1 to the end
5.	x[c(1,4,2)] specific elements
6.	x[“name”] elements named “name”
7.	x[x>3] all elements greater than 3
8.	x[x > 3 & x < 5] all elements between 3 and 5
9.	x[x %in% c(“a”,“and”,“the”)] all elements in given set

### Indexing lists
1.	x[n] list with elements n
2.	x[[n]] nt h element of the list
3.	x[[“name”]] element of the list named “name”
4.	x$name id.

Indexing matrices
1.	x[i,j] element at row i, column j
2.	x[i,] row i
3.	x[,j] column j
4.	x[,c(1,3)] columns 1 and 3
5.	x[“name”,] row named “name”

Indexing data frames (matrix indexing plus the following)
1.	x[[“name”]] column named “name”
2.	x$nameid.

Variable conversion
1.	as.data.frame(x)
2.	as.numeric(x)
3.	as.logical(x)
4.	as.character(x)

Variable information
1.	is.na(x)
2.	is.null(x)
3.	is.data.frame(x)
4.	is.numeric(x)
5.	is.character(x)
6.	length(x)
7.	dim(x)
8.	dimnames(x)
9.	nrow(x)
10.	ncol(x)
11.	class()
12.	attributes()

Data selection and manipulation
1.	which.max()
2.	which.min()
3.	which()
4.	sort()
5.	unique()
6.	table()
7.	sample()

Math
1.	max()
2.	min()
3.	range()
4.	sum()
5.	mean()
6.	median()
7.	var()
8.	sd()
9.	cor()
10.	round()
11.	abs()

Matrices
1.	t()
2.	diag()
3.	rowSums()
4.	colSums()
5.	rowMeans()
6.	colMeans()

Advanced Data processing
1.	apply()
2.	aggregate()

Strings
1.	paste()
2.	strsplit()
3.	tolower()
4.	toupper

Plotting
1.	hist()
2.	plot()

Distributions
1.	rnorm()
2.	runif()

Programming
1.	show that you can define a function
2.	show that you can write a for loop
3.	show that you can write a while loop
4.	show that you can write an if else statement
5.	Explain what return() does inside a function, show you can use it
6.	Explain what break() does, show you can use it

Installing some packages
Use the packages tab in R-studio to install these packages. You will need to be connected to the internet when you do this. If you are installing on your laptop, or on R-studio Cloud, then these packages will not need to installed again.
1.	ggplot2
2.	dplyr
3.	shiny
4.	data.table
5.	reshape2
6.	stringr

