---
title: "Journal"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

### Problem 1
Do simple math with numbers, addition, subtraction, multiplication, division
```{r}
1+1
3-2
4*6
5/7

```
# Problem 2
Put numbers into variables, do simple math on the variables

```{r}
m <-1
```
# Problem 3
Write code that will place the numbers 1 to 100 separately into a variable using for loop. Then, again using the seq function.

```{r}

```
# Problem 4
Find the sum of all the integer numbers from 1 to 100.

* Use the sum() function on a vector of numbers
* How would you do this without using the sum function? For example, how could you use a for loop to accomplish this task?

```{r}

```
# Problem 5
Write a function to find the sum of all integers between any two values.

```{r}

```
# Problem 6
List all of the odd numbers from 1 to 100.
* Use the seq() function
* How could you do this without using the seq() function? Consider using the mod function %%, which evaluates whether or not there is a remainder when dividing one number by another.
```{r}

```
# Problem 7
List all of the prime numbers from 1 to 1000.
```{r}

```
# Problem 8
Generate 100 random numbers:
* Check out the runif function
* To look at the help file run ?runif in the console. In general ?function_name will show the help file for any function in R.
# Problem 7
List all of the prime numbers from 1 to 1000.
```{r}

```
# Problem 9
Generate 100 random numbers within a specific range (runif can do this)
```{r}

```
# Problem 10
* Write your own functions to give descriptive statistics for a vector variable storing multiple numbers. Write functions for the following without using R intrinsics: mean, mode, median, range, standard deviation (It’s ok to use sum() and length() be creative and see if you can find multiple solutions. Here is an example for two ways to compute the mean.)
```{r}

```
# Problem 11
Count the number of characters in a string variable (use strsplit() to split a character vector)
```{r}

```
# Problem 12
Count the number of words in a string variable (use strsplit)
```{r}

```
# Problem 13
Count the number of sentences in a string variable (consider splitting by the . character)

```{r}

```
# Problem 14
Count the number of times a specific character occurs in a string variable
* Table() function can help count individual occurences
* How would you do this without the table function?
# Problem 12
Count the number of words in a string variable (use strsplit)
```{r}

```
# Problem 15
Do a logical test to see if one word is found within the text of another string variable.
* For example given the word hello, can you run a test to see if it is contained in the test sentence?


```{r}

```
# Problem 16
