---
title: "Journal"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

### Problem 1
Do simple math with numbers, addition, subtraction, multiplication, division
```{r}
1+1
3-2
4*6
5/7

```
# Problem 2
Put numbers into variables, do simple math on the variables

```{r}
m <-1
```
# Problem 3
A). Write code that will place the numbers 1 to 100 separately into a variable using for loop. 

```{r}
a<-0
for(i in 1:100){
  a<-a + print(i)
}
```
B). Then, again using the seq function.
```{r}
seq(1,100)
```

# Problem 4
Find the sum of all the integer numbers from 1 to 100:

A). Use the sum() function on a vector of numbers
```{r}
b<-0
for(i in 1:100){
  b<- b+sum(i)
}

```
B). How would you do this without using the sum function? For example, how could you use a for loop to accomplish this task?
```{r}
e<-0
for (i in 1:100){
e<-e + i
}

```

# Problem 5
Write a function to find the sum of all integers between any two values.

```{r}
SumFunction <- function (x) {
  f<-0
  for (i in x){
    f<-f+i
  }
  return(f)
}

x<-1:100
SumFunction(x)
```
# Problem 6
List all of the odd numbers from 1 to 100:
A). Use the seq() function

```{r}
seq(1,100, by=2)

```
B). How could you do this without using the seq() function? Consider using the mod function %%, which evaluates whether or not there is a remainder when dividing one number by another.
```{r}
for(i in 1:100){
  if (!i %%2)
next
print(i)
}

```

# Problem 7
List all of the prime numbers from 1 to 1000.
```{r}
PrimeFunction<- function(x){
    if(x==2){
        print("TRUE")
    } else {
    if(x%%(2:(x-1))!=0){
        print(seq(as.numeric("TRUE")))
    } else { 
        print("FALSE")
    }}}

PrimeFunction(x)
```
# Problem 8
Generate 100 random numbers.

```{r}
h<-runif(100)

h
```
# Problem 9
Generate 100 random numbers within a specific range (runif can do this)
```{r}
j<-runif(100,1,200)

j

```
# Problem 10
Write your own functions to give descriptive statistics for a vector variable storing multiple numbers. Write functions for the following without using R intrinsics: 
A). mean 
```{r}
MeanFunction <- function(x){
  k<-0
  l<- 0
  for(i in x){
    k <- k+sum(i)
    l<-l+length(x)
  }
  return(k/l)
}

MeanFunction(x)

```
B). mode 
```{r}
ModeFunction <- function(x){
  m<-0
  for(i in x){
    m <- m+freq(x) }
  return(m)
}
m
```
C). median 
```{r}
MedianFunction <- function(x){
 n<-0
 p<-0
  for(i in x){
    n<-n+seq(i)
    p<-p+((length(x)+1)/2)
    }
 return(p)
 }

```
D). range
```{r}
RangeFunction <- function(x){
q<-0
r<-0
for(i in x){
q <-q+min(x)
r<-r+max(x)
  }
  return(r-q)
}

RangeFunction(x)

```
E). standard deviation
```{r}
StanDevFunction <- function(x){
s<-0
for(i in x){
s <-s+sqrt(var(x))
  }
  return(s)
}
StanDevFunction(x)
```
# Problem 11
Count the number of characters in a string variable (use strsplit() to split a character vector)
```{r}
z <- "dskjfenlrhelenhtrileriwtnhreut"

t<- unlist(strsplit(z,split=""))
length(t)

```
# Problem 12
Count the number of words in a string variable (use strsplit)
```{r}
y<-"Count the number of words in a string variable use strsplit"

u<- unlist(strsplit(y,split=" "))
length(u)

```
# Problem 13
Count the number of sentences in a string variable (consider splitting by the . character)

```{r}
x<-"Count the number of sentences in a string variable. Consider splitting by the period character."

v<- unlist(strsplit(x,split="  "))
length(v)

```
# Problem 14
Count the number of times a specific character occurs in a string variable:

A). Table() function can help count individual occurences

```{r}
w<-c(2,2,3,5,6,7,8,8,8,9,0,8,6,7,5,7,6,3,6,3,4)
ab<-table(w)
as.data.frame(ab)
```
B). How would you do this without the table function?

```{r}

w<-c(2,2,3,5,6,7,8,8,8,9,0,8,6,7,5,7,6,3,6,3,4)
ab<-as.data.frame(w)
ab
```

# Problem 15
Do a logical test to see if one word is found within the text of another string variable.

```{r}
bc<-"text"
cd<-"Do a logical test to see if one word is found within the text of another string variable"

bc%in%cd
```
# Problem 16
Put the current computer time in milliseconds into a variable
```{r}

```
# Problem 17
Measure how long a piece of code takes to run by measuring the time before the code is run, and after the code is run, and taking the difference to find the total time

```{r}

```
# Problem 18
Read a .txt file or .csv file into a variable
A). scan() is a general purpose text input function

```{r}

```
B). read.csv() will read .csv files

```{r}

```

# Problem 19
Output the contents of a variable to a .txt file
*write.csv()
```{r}

```
# Problem 20
Create a variable that stores a 20x20 matrix of random numbers
* here’s how you make a matrix full of 0s


```{r}

```
# Problem 21
Output any matrix to a txt file using commas or tabs to separate column values, and new lines to separate row values
* write.csv()
