---
title: "Journal"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# Problem 1
Do simple math with numbers, addition, subtraction, multiplication, division
```{r}
1+1
3-2
4*6
5/7

```
# Problem 2
Put numbers into variables, do simple math on the variables

```{r}
m <-1
```
# Problem 3
A). Write code that will place the numbers 1 to 100 separately into a variable using for loop. 

```{r}
a<-0
for(i in 1:100){
  a<-a + print(i)
}
```
B). Then, again using the seq function.
```{r}
seq(1,100)
```

# Problem 4
Find the sum of all the integer numbers from 1 to 100:

A). Use the sum() function on a vector of numbers
```{r}
b<-0
for(i in 1:100){
  b<- b+sum(i)
}

```
B). How would you do this without using the sum function? For example, how could you use a for loop to accomplish this task?
```{r}
e<-0
for (i in 1:100){
e<-e + i
}

```

# Problem 5
Write a function to find the sum of all integers between any two values.

```{r}
SumFunction <- function (x) {
  f<-0
  for (i in x){
    f<-f+i
  }
  return(f)
}

x<-1:100
SumFunction(x)
```
# Problem 6
List all of the odd numbers from 1 to 100:
A). Use the seq() function

```{r}
seq(1,100, by=2)

```
B). How could you do this without using the seq() function? Consider using the mod function %%, which evaluates whether or not there is a remainder when dividing one number by another.
```{r}
for(i in 1:100){
  if (!i %%2)
next
print(i)
}

```

# Problem 7
List all of the prime numbers from 1 to 1000.
```{r}
PrimeFunction<-function (n){

for(i in 2:(n-1)) {
if ((n %% i) == 0) {
  print('NOT Prime Number')
} else print('YES Prime Number')
return (n)

}
}


```
# Problem 8
Generate 100 random numbers.

```{r}
h<-runif(100)

h
```
# Problem 9
Generate 100 random numbers within a specific range (runif can do this)
```{r}
j<-runif(100,1,200)

j

```
# Problem 10
Write your own functions to give descriptive statistics for a vector variable storing multiple numbers. Write functions for the following without using R intrinsics: 
A). mean 
```{r}
MeanFunction <- function(x){
  k<-0
  l<- 0
  for(i in x){
    k <- k+sum(i)
    l<-l+length(x)
  }
  return(k/l)
}

MeanFunction(x)

```
B). mode 
```{r}
ModeFunction <- function(x){
  m<-0
  for(i in x){
    m <- m+freq(x) }
  return(m)
}
m
```
C). median 
```{r}
MedianFunction <- function(x){
 n<-0
 p<-0
  for(i in x){
    n<-n+seq(i)
    p<-p+((length(x)+1)/2)
    }
 return(p)
 }

```
D). range
```{r}
RangeFunction <- function(x){
q<-0
r<-0
for(i in x){
q <-q+min(x)
r<-r+max(x)
  }
  return(r-q)
}

RangeFunction(x)

```
E). standard deviation
```{r}
StanDevFunction <- function(x){
s<-0
for(i in x){
s <-s+sqrt(var(x))
  }
  return(s)
}
StanDevFunction(x)
```
# Problem 11
Count the number of characters in a string variable (use strsplit() to split a character vector)
```{r}
z <- "dskjfenlrhelenhtrileriwtnhreut"

t<- unlist(strsplit(z,split=""))
length(t)

```
# Problem 12
Count the number of words in a string variable (use strsplit)
```{r}
y<-"Count the number of words in a string variable use strsplit"

u<- unlist(strsplit(y,split=" "))
length(u)

```
# Problem 13
Count the number of sentences in a string variable (consider splitting by the . character)

```{r}
x<-"Count the number of sentences in a string variable. Consider splitting by the period character."

v<- unlist(strsplit(x,split="  "))
length(v)

```
# Problem 14
Count the number of times a specific character occurs in a string variable:

A). Table() function can help count individual occurences

```{r}
w<-c(2,2,3,5,6,7,8,8,8,9,0,8,6,7,5,7,6,3,6,3,4)
ab<-table(w)
as.data.frame(ab)
```
B). How would you do this without the table function?

```{r}

w<-c(2,2,3,5,6,7,8,8,8,9,0,8,6,7,5,7,6,3,6,3,4)
ab<-as.data.frame(w)
ab
```

# Problem 15
Do a logical test to see if one word is found within the text of another string variable.

```{r}
bc<-"text"
cd<-"Do a logical test to see if one word is found within the text of another string variable"

bc%in%cd
```
# Problem 16
Put the current computer time in milliseconds into a variable
```{r}
print(as.numeric(Sys.time())*1000, digits=15)
```
# Problem 17
Measure how long a piece of code takes to run by measuring the time before the code is run, and after the code is run, and taking the difference to find the total time

Before
```{r}
Bb<-print(as.numeric(Sys.time())*1000, digits=15)
```
After
```{r}
Aa<-print(as.numeric(Sys.time())*1000, digits=15)
```
Difference
```{r}
AaBb<-Aa-Bb

AaBb
```
# Problem 18
Read a .txt file or .csv file into a variable. Scan() is a general purpose text input function. read.csv() will read .csv files.

```{r}
read.csv("RandomRead.csv",header = TRUE,sep = ",")
```

# Problem 19
Output the contents of a variable to a .txt file
```{r}
ds <- c(2,8,6,4,0,1,4,7)
hi<-write.csv(ds, file = "RandomRead.csv")
hi
```
# Problem 20
Create a variable that stores a 20x20 matrix of random numbers

```{r}
ef<-runif(400)

fg<-matrix(ef,nrow = 20,ncol = 20)

fg

```
# Problem 21
Output any matrix to a txt file using commas or tabs to separate column values, and new lines to separate row values
```{r,eval=FALSE}
ij<-write.csv(ef,file = "RandomRead.csv", sep="\t", row.names = TRUE, col.names = NA)
ij
```
